Supplemental Materials, Methods and Results

### 2021-05-07 supp.Rmd
reorganised figures and tables so they follow on from each other.

@@

### Changes in visual signals across body regions show similar patterns
We took measurements of spectral reflectance for different body regions of each chamaleon. In our primary analysis, we averaged across different body regions because we were interested only in whether visual signals were different in Kenya and Hawaii overall. This was justified given that, across the different body regions, effects were largely in a similar direction, and often of similar magnitude (Figures \@ref(fig:FigS1), \@ref(fig:FigS2), \@ref(fig:FigS3)) and Tables \@ref(tab:tableS1), \@ref(tab:tableS2), \@ref(tab:tableS3), \@ref(tab:tableS4). \@ref(tab:tableS5)).

```{r FigS1, fig.width = 13, fig.height = 12, fig.cap = "Chormatic (A, C) and Achromatic (B, D) contrast in just noticible differences (JND) for Hawaiian and Kenyan lizards relative to their environments. All four body regions (gular, mid-flank, tailbase and topflank) are shown averaged across stems and leaves found in their habitat. Mean JNDs are provided along with 95% confidence intervals. A & B represent male-male contest displays whereas C & D represent courtship displays"}

@@

```{r tableS2, tab.cap = "Wald Tests comparing significance of model parameters. Wald tests computed using robust variance estimators with a Saitterwaite correction to the degrees of freedom. Interactions were first tested and models refit to test the signifiacnce of main effects"}
fullTable <- rbind(wald_table_ConspicDisplayAC, 
                   wald_table_ConspicDisplayCC, 
                   wald_table_ConspicCourtshipAC,
                   wald_table_ConspicCourtshipCC)

@@

```{r tableS3, tab.cap = "Linear mixed effects model results using sandwich estimators and Saitterwaite degrees of freedom correction.Social Context"}
robust_sc_table <- rbind(robust_ConspicDisplayAC,
                          robust_ConspicDisplayCC,
                          robust_ConspicCourtshipAC,
                          robust_ConspicCourtshipCC) %>% 
                    mutate(p_Satt = sapply(p_Satt, function(x) p_value(x)),
                           SocialContext = c("Male-Male Display", rep("", 17), 
                                             "Courtship Display", rep("", 17)),
                           JND = c("Achromatic Contrast", rep("", 8), 
                                   "Chromatic Contrast", rep("", 8), 
                                   "Achromatic Contrast", rep("", 8), 
                                   "Chromatic Contrast", rep("", 8)))

@@

```{r FigS2, fig.width = 12, fig.height = 12, fig.cap = "Predators All four body regions (gular, mid-flank, tailbase and topflank) are shown averaged across stems and leaves found in their habitat. Mean JNDs are provided along with 95% confidence intervals. A & B represent male-male contest displays whereas C & D represent courtship displays"}

@@

```{r tableS4, tab.cap = "Wald Tests comparing significance of model parameters for predators. Wald tests computed using robust variance estimators with a Saitterwaite correction to the degrees of freedom. Interactions were first tested and models refit to test the signifiacnce of main effects"}

@@

```{r tableS5, tab.cap = "Linear mixed effects model results using sandwich estimators and Saitterwaite degrees of freedom correction.Predators"}
robust_sc_pred_table <- rbind(robust_PredatorAC,
                         robust_PredatorCC) %>% 
                    mutate(p_Satt = sapply(p_Satt, function(x) p_value(x)),
                           JND = c("Achromatic Contrast", rep("", 9), 
                                   "Chromatic Contrast", rep("", 9)))

@@

@@

```{r tableS7, tab.cap = "Pairwise comparisons of achormatic contrast between Kenyan and Hawaiian chameleon displays to a snake and bird visual system. Four different body regions ('gular', 'midflank', 'tailbase', topflank') are provided along with pairwise Wald test for contrast significance. Wald test uses a robust variance correction on the standard errors."}

@@

```{r FigS3, fig.width = 13, fig.height = 7.5, fig.cap = "Local adaptation. All four body regions (gular, mid-flank, tailbase and topflank) are shown averaged across stems and leaves found in their habitat. Mean JNDs are provided along with 95% confidence intervals. A & B represent male-male contest displays whereas C & D represent courtship displays"}
# Courship data

@@

```{r FigS4, fig.cap = "Examples of chameleon colour signal change in response to different social and predatory contexts"}

>>>>

```{r FigS1, fig.cap = "Examples of chameleon colour signal change in response to different social and predatory contexts"}

@@

## Assessing changes in sexual signals across different body regions
We took measurements of spectral reflectance for different body regions of each chamaleon. In our primary analysis, we averaged across different body regions because we were interested only in whether visual signals overall were different between Kenya and Hawaii. This was justified given that, across the different body regions, effects were largely in a similar direction, and often of similar magnitude (Figures \@ref(fig:FigS2), \@ref(fig:FigS3), \@ref(fig:FigS4) and Tables \@ref(tab:tableS1), \@ref(tab:tableS2), \@ref(tab:tableS3), \@ref(tab:tableS4). \@ref(tab:tableS5)).

#### Body regions in social contexts (Male-male and Courtship Display) show different magnitude of responses, but similar directionality

```{r FigS2, fig.width = 13, fig.height = 12, fig.cap = "Chormatic (A, C) and Achromatic (B, D) contrast in just noticible differences (JND) for Hawaiian and Kenyan lizards relative to their environments. All four body regions (gular, mid-flank, tailbase and topflank) are shown averaged across stems and leaves found in their habitat. Mean JNDs are provided along with 95% confidence intervals. A & B represent male-male contest displays whereas C & D represent courtship displays"}

@@

```{r tableS1, tab.cap = "Wald Tests comparing significance of model parameters. Wald tests computed using robust variance estimators with a Saitterwaite correction to the degrees of freedom. Interactions were first tested and models refit to test the signifiacnce of main effects"}
fullTable <- rbind(wald_table_ConspicDisplayAC, 
                   wald_table_ConspicDisplayCC, 
                   wald_table_ConspicCourtshipAC,
                   wald_table_ConspicCourtshipCC)

@@

```{r tableS2, tab.cap = "Linear mixed effects model results using sandwich estimators and Saitterwaite degrees of freedom correction.Social Context"}
robust_sc_table <- rbind(robust_ConspicDisplayAC,
                          robust_ConspicDisplayCC,
                          robust_ConspicCourtshipAC,
                          robust_ConspicCourtshipCC) %>% 
                    mutate(p_Satt = sapply(p_Satt, function(x) p_value(x)),
                           SocialContext = c("Male-Male Display", rep("", 17), 
                                             "Courtship Display", rep("", 17)),
                           JND = c("Achromatic Contrast", rep("", 8), 
                                   "Chromatic Contrast", rep("", 8), 
                                   "Achromatic Contrast", rep("", 8), 
                                   "Chromatic Contrast", rep("", 8)))

@@

```{r FigS3, fig.width = 12, fig.height = 12, fig.cap = "Predators All four body regions (gular, mid-flank, tailbase and topflank) are shown averaged across stems and leaves found in their habitat. Mean JNDs are provided along with 95% confidence intervals. A & B represent male-male contest displays whereas C & D represent courtship displays"}

@@

```{r tableS3, tab.cap = "Wald Tests comparing significance of model parameters for predators. Wald tests computed using robust variance estimators with a Saitterwaite correction to the degrees of freedom. Interactions were first tested and models refit to test the signifiacnce of main effects"}

@@

```{r tableS4, tab.cap = "Linear mixed effects model results using sandwich estimators and Saitterwaite degrees of freedom correction.Predators"}
robust_sc_pred_table <- rbind(robust_PredatorAC,
                         robust_PredatorCC) %>% 
                    mutate(p_Satt = sapply(p_Satt, function(x) p_value(x)),
                           JND = c("Achromatic Contrast", rep("", 9), 
                                   "Chromatic Contrast", rep("", 9)))

@@

```{r tableS5, tab.cap = "Pairwise comparisons of achormatic contrast between Kenyan and Hawaiian chameleon displays to a snake and bird visual system. Four different body regions ('gular', 'midflank', 'tailbase', topflank') are provided along with pairwise Wald test for contrast significance. Wald test uses a robust variance correction on the standard errors."}

@@

@@

```{r FigS4, fig.width = 13, fig.height = 7.5, fig.cap = "Local adaptation. All four body regions (gular, mid-flank, tailbase and topflank) are shown averaged across stems and leaves found in their habitat. Mean JNDs are provided along with 95% confidence intervals. A & B represent male-male contest displays whereas C & D represent courtship displays"}
# Courship data

@@
